DNNNNR0: How to Avoid OOTA Without Really Trying

### 2025-05-10 paper/rebuttal-mods.txt

x	Be less condescending towards Mark Batty.  Maybe
	s/is persisting with/is working on/.

x	Add a Section 1.3 ("Our Approach"?) that summarizes the
	rfe/sdep/non-sdep-dep approach and emphasizes proving
	OOTA cannot happen as opposed to an exact delineation
	between sdep and non-sdep.

x	Add citations to later sections that discuss litmus tests
	that are similar to those in the literature.

x	Consider adding a 2.2.x section that discusses the difficulties
	inherent in computing sdep for function calls, especially when
	the function will be part of a dynamic library that has not yet
	been written.  (This addresses Reviewer #72F's call for handling
	examples in Section 5 of [5].)  Or put this in a later section
	demonstrating how we handle the various litmus tests.

@@

x	On page 9, "While it possible".  [ Since fixed by Alan. ]

x	In Section 7.4 ("Merging Quasi-Volatile Loads"), change focus
	from intuitive notions to a community-process approach for
	determining what optimizations are legitimate.  Math cannot
	handle this.  We avoid the problem by looking at the compiler
	implementation, which is downstream of the community process.

x	Also in Section 7.4 change "our intuitive notions" to "one's
	intuitive notions".

x	Add a section before Section 7 ("Issues and Refinements") that
	shows how our approach handles a few well-known examples of OOTA.
	This needs to be in greater detail than in the "Causality Test
	Cases" discussions in P3064R2 ("How to Avoid OOTA Without Really
	Trying").

### 2025-05-11 paper/ootavacuous.tex
ootavacuous: Move history section to front
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

@@

This paper is a condensation of P3064R2 ("How to Avoid OOTA Without
Really Trying")~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying}.
It also adds citations and clarifications.

>>>>

This paper is a condensation of P3064R2 ("How to Avoid OOTA Without
Really Trying")~\cite{PaulEMcKenney2023P3046R2/OOTAwithoutTrying},
which was criticized as being too long.
It also adds citations and clarifications.

@@
